Reanalysis Step 9: Alternative Propensity Score Specifications

### 2025-09-05 reanalysis-9-alternative_specifications.qmd
bug fix gbm

# Define completed methods (add to this list as methods complete successfully)
completed_methods <- c(
  "nearest_glm"  # Uncomment if completed
)

>>>>

# Define completed methods (add to this list as methods complete successfully)
completed_methods <- c(
  "nearest_glm",  # Uncomment if completed
  "nearest_gam"
  # "nearest_gbm",
  # "nearest_lasso",
  # "nearest_rpart",
  # "nearest_mahalanobis",
  # "subclass_glm",
  # "cbps",
  # "entropy",
  # "bart",
  # "twang_gbm"
)
